%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[super]{nth}
\usepackage{parcolumns}\usepackage{hyperref} 
 \hypersetup{ 
     colorlinks=true, 
     linkcolor=blue, 
     filecolor=blue, 
     citecolor = black,       
     urlcolor=blue, 
     } 
\usepackage{fancyhdr}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingV}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\fancyhf{}
\fancyfoot[L]{\today}
\pagestyle{fancy}
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape ABDELRAHMAN A. MAHMOUD} \\ \vspace{1pt}
    \small Nasr City, Cairo, Egypt  $|$ +20 1270535270 \\ \vspace{1pt} \href{a.a.mahmoud1170@gmail.com}{\underline{a.a.mahmoud1170@gmail.com }} $|$ 
    \href{https://www.linkedin.com/in/abdelrahman-ashraf-869998221/}{\underline{linkedin.com/in/abdelrahman}} $|$
    \href{https://github.com/Abdu117}{\underline{github.com/Abdu117}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Helwan University} {Cario, Egypt}
      { BSc. Computer Engineering, Cumulative Grade: \textbf{Distinct (88.5\%)}}{Sep 2020 - Jul 2025}
        \resumeItemListStart
        \resumeItem{\textbf {Coursework}: Data Structures \& Algorithms, Database Systems, Discrete Math, Statistics \& Probability, Numerical Analysis, Microprocessor \& Microcontroller, Software Engineering, VLSI Design \& Simulation.}
        
      \resumeItem{  \textbf {Honors}: Ranked \nth{1} out of 113 students in freshman year and \nth{4} out of 1000+ students in the prep year.}
        
        \resumeItem{  \textbf{Leadership \& Extracurriculars}: Provided sessions teaching basics C programming language in GDSC Helwan, Collaborated with Launtech community to develop and maintain Embedded Systems projects.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd     


%-----------EXPERIENCE----------- 

\section{Experience} 
\resumeSubHeadingListStart
\resumeSubheading
  {Embedded Systems Intern}{Aug 2023}
  {Information Technology Institute (ITI)}{Cairo, Egypt}
  \resumeItemListStart
    \resumeItem{Acquired in-depth knowledge of \textbf{ARM} architecture focusing on \textbf{ARM Cortex-M3} and \textbf{M4}, and successfully leveraged this understanding to design and implement a compelling project.}
    \resumeItem{
     Proficiently applied concepts encompassing \textbf{Stacking}, \textbf{Exceptions}, \textbf{NVIC}, \textbf{DMA}, and \textbf{SysTick} demonstrating \\ a comprehensive understanding of diverse embedded systems components and functionalities.}
    \resumeItem{Acquired a comprehensive understanding of teamwork dynamics and project integration processes through hands-on tools like \textbf{Git extensions}, ensuring efficient version control and collaboration.}
    
    
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Door Locker Security System} $|$ \emph{C \href{https://github.com/Abdu117/Door_locker_security_system_using_ATmega32}{\underline{Github}}}}{Nov 2022}
          \resumeItemListStart
            \resumeItem{Implemented a door locker system based on a layered architecture (MCAL, HAL, App) using AVR(Atmega32).}
             \resumeItem{Utilized Embedded C to develop synchronous and timeout functions to prevent brute-force attacks and enhance system reliability.}
            \resumeItem{Main Drivers used: UART, I2C, SPI, EEPROM, Keypad.}
          
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{SwiftPay} $|$ \emph{Java, SQL \href{https://github.com/Abdu117/SwiftPay_Billing_System}{\underline{Github}}}}{May 2023}
          \resumeItemListStart
            \resumeItem{Developed a GUI billing system application, backed by MS SQL Server and JDBC API.}
            \resumeItem{
            Created customization options, enabling cashiers to generate customer bills and view and edit stock products.}
             \resumeItem{
   Integrated interactive charts and graphs to provide users with real-time, visually informative statistics about product sales.        
           }
          \resumeItemListEnd

     \resumeProjectHeading
          {\textbf{Launtech Website} $|$ \emph{HTML/CSS, Javascript, PHP, MySQL \href{https://github.com/Abdu117/LaunTech_website_project}{\underline{Github}}}}{Jul 2022}
          \resumeItemListStart
            \resumeItem{Designed a website to facilitate discovering and joining Launtech community.}
           
          \resumeItemListEnd
          
  \resumeProjectHeading
          {\textbf{16-Bit MIPS Processor} $|$ \emph{VHDL, Vivado \href{https://github.com/Abdu117/MIPS_processor_using_VHDL}{\underline{Github}}}}{Dec 2022}
          \resumeItemListStart
            \resumeItem{
            Created MIPS processor using VHDL, implementing pipelined architecture and supporting MIPS base instructions.}\\ \vspace{1pt}
             \resumeItem{ Developed to perform 16 different operations besides 8 different arithmetic operations.}
 \resumeItem{Integrated the processor with an FPGA board for simulation.
}
           
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd


%-----------HONERS-----------
\section{Honors and Accomplishments}
\resumeSubHeadingListStart
      \resumeSubheadingV
      {National Finalist at NASA Space Apps} {Oct 2023}\vspace{1pt}
            \resumeSubheadingV
      {National Finalist at Regeneron International Science and Engineering Fair}{Feb 2020}\vspace{1pt}
            \resumeSubheadingV
    {International Finalist at Intel International Science and Engineering Fair (Intel ISEF)} {May 2019}
    \resumeItemListStart
            \resumeItem{Ranked \nth{1} in the Chemical Energy Category and \nth{3} overall at Intel National Science Fair.}
            \resumeItem{Qualified for and attended the international fair as Egypt’s representative in Phoenix, Arizona, USA.}
            \resumeItemListEnd

    \resumeSubheadingV{International Finalist at Nasser Bin Hamad (NBH) Award}{Oct 2017}
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Embedded C, Python, Java, HTML/CSS, Javascript, SQL, VHDL} \\
     \textbf{Tools}{: VS Code, Eclipse, MS SQL Server, Git, Linux, Proteus, OOP \& Functional Programming, AVR (Atmega32), ARM (STM32f103 \& STM32f44re), STM32CubeIDE, Keil, Quartus Prime, FPGA} \\
     \textbf{Technologies}{: NodeJs, MongoDB, ExpressJs}
  
    }}
 \end{itemize}


\end{document}